\documentclass{common/cs157}
\usepackage{hyperref}
% \usepackage{clrscode}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{listings}


\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage[noframe]{showframe}
\usepackage{framed}
\usepackage[shortlabels]{enumitem}

\renewenvironment{shaded}{%
  \def\FrameCommand{\fboxsep=\FrameSep \colorbox{shadecolor}}%
  \MakeFramed{\advance\hsize-\width \FrameRestore\FrameRestore}}%
 {\endMakeFramed}
\definecolor{shadecolor}{gray}{0.9}


% comment this in if you want to compile the solution key:
% \sol


\hwk{0}
\due{Sep.\ 23, 2021}


\begin{document}

Hi everyone, welcome to CS1570! Some action items to get you started with the course:
\begin{enumerate}[1.]
    \item You can find the course website at \url{https://cs157-2021.github.io}, where homeworks and hours information will be located. Note that \url{http://cs.brown.edu/courses/csci1570} redirects you to the correct site.
    \item Join the course Gradescope at \url{www.gradescope.com} with the code \textbf{D5G63D}.
    \item Join the course Ed page at \url{https://edstem.org/us/courses/12570}. You can log in to Ed using your Brown credentials. Make sure to keep an eye on this discussion page as we will upload lectures and maintain FAQ threads for the homeworks on here.
    \item If you will be using an anonymous id on Gradescope this semester (an updated guide on creating one can be found under the \underline{\href{https://cs157-2021.github.io/resources.html}{resources}} tab on the course website), please fill out the following form at \url{https://forms.gle/gDbAnbAWwZfyc2gt5}.
    \item Read the collaboration policy on the course syllabus (also on the \underline{\href{https://cs157-2021.github.io/resources.html}{resources}} page of the course website). There is space for you to include a signature at the bottom of the pdf, so just submit a signed copy of the syllabus on Gradescope under the \textbf{Homework 0} assignment :).
\end{enumerate}
Finally, if you have any feedback for the course, there is an \underline{\href{https://forms.gle/GQCHj9WdobTootCT7}{anonymous feedback form}} located on the homepage of the course website. We would love to hear from you!

\end{document}