\documentclass{common/cs157}

\hwk{2}
\due{September 27, 2022 - 14:30 ET}

\begin{document}

\homeworkhandin 

\begin{problem}{1}
\begin{enumerate}
    \item Assume that we want to sort sequences of numbers with the following property:\\
    \textbf{P:} ``Each element in the input sequence is placed in the input at most $k$ locations away from its placement in the output ordered sequence''. \\
    Design a modification of Selection sort which runs in time $O(nk)$.
    \item Analyze the worst-case running time of Insertion Sort for strings with the $\textbf{P}$ property.
    \item For input sequences exhibiting property \textbf{P}, which of Mergesort, Insertion Sort, or Standard Selection sort would you use for better performance? How does your choice change for different values of $k$? Motivate your answer. 
    \item Assume now that we are looking to sort input sequences in which there is a subsequence of size $k$ which is already sorted. Show that using one among Selection, Insertion, or Bubble sort it is possible to sort such inputs in $O(n(n-k))$ steps.
\end{enumerate}
\end{problem}

\newpage

\begin{problem}{2}
Joanna is in charge of a law firm working on an important case, where she needs to find a specific folder which is stored in one of the company filing cabinets. She assigns this task to Rohit the Paralegal. 
\\\\
Rohit has at most $N$ workers at his disposal to complete this task. The filing cabinet has $M$ shelves, and each shelf has $F_i$ folders. Assume that there are always more shelves than Rohit has workers. Joanna wants to minimize chaos, so she asks Rohit to assign workers to a contiguous sub-array of shelves. 
\\\\
Rohit wants to divide the work as evenly as possible among the workers. Help Rohit come up with an algorithm to find the \textbf{minimum number of folders} that each of his workers has to look at in order to find the specific folder.\\ 
\\
Since Joanna is a strict boss, please give an algorithm that runs in $O(M\log(S))$, where $S$ is the total number of folders in the entire filing cabinet.
\end{problem}

\newpage

\begin{problem}{3}
Let $S$ be an array of $n$ unique integers. An
inversion in S is a pair of indices $i$ and $j$ such that $i<j$ but $S[i] > S[j]$. Describe an algorithm running in $O(n \log{n})$ time for determining the number of inversions in $S$.
\end{problem}

\end{document}