\documentclass{common/cs157}

\hwk{3}
\due{October 4, 2022 at 14:30 ET}

\begin{document}

\homeworkhandin 

\begin{problem}{1}
\begin{enumerate}
    \item Let $E$ be the set of edges of a finite undirected graph and $\ell$ be the collection of subsets of $E$ such that $A \in \ell$ if and only if $A$ is an acyclic subset of $E$. Show that the ordered pair $(E, \ell)$ is a matroid. 
    
    \item Let $w:E \rightarrow \mathbb{R}^+$ be a function that assigns a non-negative weight to each element of $E$. Given a subroutine that takes as inputs an edge $(u,v)$ in $E$ and an acyclic subset $A$ of $E$, and returns $true$ if $A \cup {(u,v)}$ is acyclic and $false$ otherwise, design an efficient algorithm to find an acyclic subset of $E$ of maximum weight. Analyze its runtime and argue the correctness/optimality.
\end{enumerate}
\end{problem}

\newpage

\begin{problem}{2}
A \emph{subsequence} of $[a_1, a_2, \cdots, a_n]$ is a list of numbers $[a_{i_1}, a_{i_2}, \cdots, a_{i_k}]$ such that $i_1 < i_2 < \cdots < i_k$.

Consider the list $[5, 1, 6, 2, 3, 10, 11]$. Two strictly increasing subsequences are given by $[5, 6, 10]$ and $[1, 2, 3, 10, 11]$. Moreover, $[1, 2, 3, 10, 11]$ is the longest strictly increasing subsequence of this list of numbers.

\begin{enumerate}
    \item Given an arbitrary list of numbers, design a greedy algorithm to determine the length of the longest strictly increasing subsequence. Your algorithm should run in $O(n\log{n})$ time where $n$ is the length of the input list. Analyze the runtime of your algorithm and argue correctness/optimality.
    
    \item Modify your algorithm to instead output the longest increasing subsequence of the original list of numbers. In the case of multiple longest increasing subsequences, outputting any of them shall suffice. Argue the correctness of your modified algorithm.
\end{enumerate}
\end{problem}

\end{document}